State Results

### 2023-07-10 reports/county_figures.Rmd
update manuscript

@@

```{r}
plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  theme(strip.text.x = element_text(size=12)) +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations with Wastewater Concentrations")

@@

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c() +
  theme(strip.text.x = element_text(size=12)) +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations with Covidestim Infections")

@@

@@

###########################################################################
# plot relationship between ratio of estimated cases to observed 
# against testing rate 
###########################################################################
county %>%
  ggplot(aes(x=total/population, y = exp_cases_median/positive)) +
  geom_point(alpha=.03, size=.9) +
  facet_wrap(~vlabel,
               labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  theme_c(axis.text.x = element_text(size =9),
          axis.title = element_text(size=16) ) +
  theme(strip.text.x = element_text(size=11, color="white")) +
  scale_y_continuous(n.breaks=10) +
  geom_hline(yintercept=1, linetype=2,color="darkred", alpha=.8, linewidth=.5) +
  labs(y = "Ratio of Estimated Infections to Observed Infections",
       x = "Testing Rate",
       subtitle = "All Time Intervals for Counties in Massachusetts",
       title = "Relationship Between Testing Rate and\nRatio of Estimated Infections to Observed Infections")+
  scale_x_continuous(limits=c(lb,.3), n.breaks=6)

>>>>

w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  
               label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=2,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c(axis.title = element_text(size=15),
          strip.text=element_text(size=15, color='white', margin=margin(2,0,2,0))) +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations Between Probabilistic Bias Infections\nand Mean Wastewater Concentration")

@@

```{r}
plt_wastewater_pb <- w_data %>%
  group_by(version) %>%
  ggplot(aes(x=exp_cases_median_std, y = mean_conc_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = mean_conc_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= correlations ) +
  facet_wrap(~vlabel,
             ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
  theme_c(axis.title = element_text(size=15),
          strip.text=element_text(size=15, color='white',margin=margin(2,0,2,0))) +
 # theme(strip.text.x = element_text(size=12)) +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Mean Wastewater Concentration\n(Standardized by County)",
       title = "Correlations with Wastewater Concentrations")

@@

plt_covidestim_pb <- w_data %>%
  ggplot(aes(x=exp_cases_median_std, y = infections_std)) +
  geom_point(alpha=.5) +
  geom_linerange(aes(xmin = exp_cases_lb_std,
                     xmax=exp_cases_ub_std, 
                     y = infections_std),
                 alpha = .3) +
  geom_text(
           aes(x=x,y=y,  label=paste0("Correlation: ", 
                                      round(Correlation,3))), 
                data= covidestim_correlations ) +
  facet_wrap(~vlabel,
              ncol=1,
             labeller= as_labeller(TeX, 
                                   default = label_parsed)) +
 theme_c(axis.title = element_text(size=15),
          strip.text=element_text(size=15, color='white',margin=margin(2,0,2,0))) +
 # theme(strip.text.x = element_text(size=12)) +
  labs(x = "Probabilistic Bias Infections\n(Standardized by County)",
       y = "Covidestim Estimates\n(Standardized by County)",
       title = "Correlations with Covidestim Infections")

@@

cat("Maximum ratio, on average, occured: ")
county %>% 
  filter(version=="v7") %>% 
  group_by(biweek) %>% 
  summarize(m = mean(exp_cases_median/positive),dates=paste(range(date),collapse=",")) %>%
  slice_max(n=1, m)

@@

###########################################################################
# plot relationship between ratio of estimated cases to observed 
# against testing rate 
###########################################################################
county %>%
  ggplot(aes(x=total/population, y = exp_cases_median/positive)) +
  geom_point(alpha=.03, size=.9) +
  facet_wrap(~vlabel,
               labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  theme_c(axis.text.x = element_text(size =9),
          axis.title = element_text(size=16) ) +
  theme(strip.text.x = element_text(size=11, color="white")) +
  scale_y_continuous(n.breaks=10) +
  geom_hline(yintercept=1, linetype=2,color="darkred", alpha=.8, linewidth=.5) +
  labs(y = "Ratio of Estimated Infections\nto Observed Infections",
       x = "Testing Rate",
       subtitle = "All Time Intervals for Counties in Massachusetts",
       title = "Relationship Between Testing Rate and\nRatio of Estimated Infections to Observed Infections")+
  scale_x_continuous(limits=c(lb,.3), n.breaks=6)

### 2023-07-10 reports/priors.Rmd
update manuscript

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)

@@

@@

ctis_smoothed  %>%
  mutate(state=toupper(state)) %>%
  select(date,
         state, 
         contains("s_untested")) %>%
  pivot_longer(contains("s_untested")) %>%
  mutate(name = case_when(
    name == "s_untested_smoothed" ~ "LOESS smoothed",
    name == "imputed_s_untested" ~ "Survey Value"
  )) %>%
  ggplot(aes(x=date, y=value, color = name, 
             alpha = name, linewidth=name)) +
  geom_line() +
  facet_wrap(~state, ncol=4) +
  scale_alpha_manual(values=c("LOESS smoothed" = .9, 
                              "Survey Value"=.6),
                     name='') +
  scale_linewidth_manual(values = c("LOESS smoothed" = 1.02, 
                              "Survey Value"=.9)) +
  scale_color_manual(values=c("Survey Value" ="black", "LOESS smoothed"="darkred"),
                     name ='') +
  guides(alpha="none",
         linewidth="none",
         color = guide_legend(override.aes = list(
           linewidth = 3,
           alpha = c("LOESS smoothed" = .9, 
                     "Survey Value"=.3)),
                            nrow=3)) +
  theme_c(legend.position="top") +
  scale_x_date(date_breaks="3 months",
               date_labels = "%b %Y") + 
  labs(y = TeX("Survey Estimate of $Pr(S_1|untested)$"),
       x= "",
       title = TeX("Comparing Approaches for Smoothing Survey Estimates of $Pr(S_1|untested)$"))

@@

```{r, fig.width=9,fig.height=9}

@@

plt1 <- theta %>% 
  filter(name != "$M(\\theta) = Pr(S_0|test+,untested)$" & name !=  "$Pr(S_0|test+,untested)$") %>%
  ggplot() +
  geom_ribbon(aes(x=x, ymin=0, ymax= value, fill='Before Melding'),alpha=.7, color=NA)+
  geom_density(aes(x=value, fill = 'After Melding'), 
               color=NA,
               data = melded_long[melded_long$name !=
                                    "$Pr(S_0|test+,untested)$",]) +
  facet_wrap(~name,
             labeller=  as_labeller(TeX, default = label_parsed),
             ncol = 3, scales="free_y") +
  theme_c()+
  theme(legend.position="right",
          axis.text.x=element_text(size=6),
          axis.title.x=element_text(size=12),
          axis.title.y=element_text(size=12)) +
  theme(legend.position="none") +
  scale_x_continuous(n.breaks=5) +
  labs(x="Value")+
scale_fill_manual(values = c("Before Melding"= "#5670BF", "Induced" = "#B28542",
                                 "After Melding" = "#418F6A"))

@@

plt2 <- theta %>% 
  filter(name==  "$Pr(S_0|test+,untested)$") %>%
  ggplot() +
  geom_ribbon(aes(x=x, ymin=0, ymax= value, fill='Before Melding'),alpha=.7)+
  geom_density(aes(x=value, fill = 'After Melding'),
               alpha=.7,color=NA,
               data = melded_long[melded_long$name ==
                                    "$Pr(S_0|test+,untested)$",]) +
    geom_density(aes(x= phi_induced, fill="Induced"), 
                 color = NA,
                 data = theta_samp,
                 alpha =.7) +
  facet_wrap(~name,
             labeller=  as_labeller(TeX, default = label_parsed),
             ncol = 3, scales="free_y") +
  theme_c() +
  theme(legend.position="right",
          axis.text.x=element_text(size=6),
          axis.title.x=element_text(size=12),
          axis.title.y=element_text(size=12))+
  scale_x_continuous(n.breaks=5, limits =c(0,1)) +
  labs(x="Value",
       fill = "")+
    scale_fill_manual(values = c("Before Melding"= "#5670BF", "Induced" = "#B28542",
                                 "After Melding" = "#418F6A"))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, cache=TRUE)

@@

```{r beta-spline-smoothed,fig.cap="The ratio of the screening test positivity over the overall test positivity from the COVID-19 Trends and Impact Survey is taken to be the estimate of $\\beta$. Because of the noise present inthe data, we use the spline smoothed values to inform the priors. More specifically, we use cubic spline smoothing with 2 knots (July 15th, 2021 and December 1st, 2021).", fig.width=12,fig.height=12}

num_states <- ctis_smoothed  %>%
  filter(keep) %>%
  pull(state) %>%
  unique() %>%
  length()

cat("There are", num_states, "states with sufficient data available to estimate $\\beta$ across the time period considered.")

ctis_smoothed  %>%
  filter(keep) %>%
  mutate(state=toupper(state)) %>%
  select(date,
         state, 
         imputed_beta,
        # beta_estimate_smoothed, 
         beta_estimate_spline_smoothed) %>%
  pivot_longer(contains("beta")) %>%
  mutate(name = case_when(
    name == "beta_estimate_spline_smoothed" ~ "Spline smoothed",
    name == "imputed_beta" ~ "Survey Value"
  )) %>%
  ggplot(aes(x=date, y=value, color = name, 
             alpha = name, linewidth=name)) +
  geom_line() +
  facet_wrap(~state, ncol=4) +
  scale_alpha_manual(values=c(
                            "Spline smoothed" = .9, 
                              "Survey Value"=.3),
                     name='') +
  scale_linewidth_manual(values = c(
                            "Spline smoothed" = 1.05, 
                              "Survey Value"=.5)) +
  scale_color_manual(values=c("#3381FF", "#26900F"),
                     name ='') +
  guides(alpha="none",
         linewidth="none",
         color = guide_legend(override.aes = list(linewidth = 3,
                                                  alpha = c(
                            "Spline smoothed" = .9, 
                              "Survey Value"=.3)),
                            nrow=3)) +
  theme_c(legend.position="top") +
  ylim(0,1) +
  scale_x_date(date_breaks="3 months",
               date_labels = "%b %Y") + 
  labs(y = TeX("Survey Estimate of $\\beta$"),
       x= "",
       title = TeX("Smoothing Survey Estimates of $\\beta$"))

ggsave(here('figures/smoothing-beta.pdf'))

@@

ctis_smoothed  %>%
  mutate(state=toupper(state)) %>%
  select(date,
         state, 
         contains("s_untested")) %>%
  pivot_longer(contains("s_untested")) %>%
  mutate(name = case_when(
    name == "s_untested_smoothed" ~ "LOESS smoothed",
    name == "imputed_s_untested" ~ "Survey Value"
  )) %>%
  ggplot(aes(x=date, y=value, color = name, 
             alpha = name, linewidth=name)) +
  geom_line() +
  facet_wrap(~state, ncol=4) +
  scale_alpha_manual(values=c("LOESS smoothed" = .9, 
                              "Survey Value"=.6),
                     name='') +
  scale_linewidth_manual(values = c("LOESS smoothed" = 1.02, 
                              "Survey Value"=.9)) +
  scale_color_manual(values=c("Survey Value" = "#26900F",
                              "LOESS smoothed"="#3381FF"),
                     name ='') +
  guides(alpha="none",
         linewidth="none",
         color = guide_legend(override.aes = list(
           linewidth = 3,
           alpha = c("LOESS smoothed" = .9, 
                     "Survey Value"=.3)),
                            nrow=3)) +
  theme_c(legend.position="top") +
  scale_x_date(date_breaks="3 months",
               date_labels = "%b %Y") + 
  labs(y = TeX("Survey Estimate of $Pr(S_1|untested)$"),
       x= "",
       title = TeX("Smoothing Survey Estimates of $Pr(S_1|untested)$"))

ggsave(here('figures/smoothing-s-untested.pdf'))

@@

```{r, fig.width=9,fig.height=6}

@@

plt1 <- theta %>% 
  filter(name != "$M(\\theta) = Pr(S_0|test+,untested)$" & name !=  "$Pr(S_0|test+,untested)$") %>%
  ggplot() +
  geom_ribbon(aes(x=x, ymin=0, ymax= value, fill='Before Melding'),alpha=.7, color=NA)+
  geom_density(aes(x=value, fill = 'After Melding'), 
               color=NA,
               data = melded_long[melded_long$name !=
                                    "$Pr(S_0|test+,untested)$",]) +
    geom_point(aes(x=1,y=0),size=0, color=NA) +
  facet_wrap(~name,
             labeller=  as_labeller(TeX, default = label_parsed),
             ncol = 3, scales="free") +
  theme_c()+
  theme(legend.position="right",
          axis.text.x=element_text(size=6),
          axis.title.x=element_text(size=12),
          axis.title.y=element_text(size=12)) +
  theme(legend.position="none") +
  scale_x_continuous(n.breaks=5) +
  labs(x="Value")+
scale_fill_manual(values = c("Before Melding"= "#5670BF", "Induced" = "#B28542",
                                 "After Melding" = "#418F6A"))

@@

plt2 <- theta %>% 
  filter(name==  "$Pr(S_0|test+,untested)$") %>%
  ggplot() +
  geom_ribbon(aes(x=x, ymin=0, ymax= value, fill='Before Melding'),alpha=.7)+
  geom_density(aes(x=value, fill = 'After Melding'),
               alpha=.7,color=NA,
               data = melded_long[melded_long$name ==
                                    "$Pr(S_0|test+,untested)$",]) +
    geom_density(aes(x= phi_induced, fill="Induced"), 
                 color = NA,
                 data = theta_samp,
                 alpha =.7) +
  facet_wrap(~name,
             labeller=  as_labeller(TeX, default = label_parsed),
             ncol = 3, scales="free") +
  theme_c() +
  theme(legend.position="right",
          axis.text.x=element_text(size=6),
          axis.title.x=element_text(size=12),
          axis.title.y=element_text(size=12))+
  scale_x_continuous(n.breaks=5, limits =c(0,1)) +
  labs(x="Value",
       fill = "")+
    scale_fill_manual(values = c("Before Melding"= "#5670BF", 
                                 "Induced" = "#B28542",
                                 "After Melding" = "#418F6A"))

### 2023-07-10 reports/state_figures.Rmd
update county figures
update manuscript

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning=FALSE,cache=FALSE)

@@

```{r, fig.height=14, fig.width=11}

subset %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = vlabel),
             alpha = .8,
             show.legend=FALSE) +
  geom_ribbon(aes(x = date,
                  fill = 'Covidestim',
                  ymin = infections.lo,
                  ymax = infections.hi),
              alpha = .6) +
  facet_wrap(~name, ncol=4, scales = "free",
              labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3.5 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x=element_text(size=5),
          axis.text.y = element_text(size=4.5),
          legend.position = "top",
          legend.text=element_text(size=12),
          strip.text.x=element_text(size=8,
                                    face='plain',
                                    color='white')) +
  scale_fill_manual(values =pal,
                    labels = TeX(names(pal)),
                    name=''
                    #,
                  # , breaks="Covidestim"
                    )  +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by State")) +
  guides(color = guide_legend(override.aes = list(linewidth =2),
                              nrow=2,
                              byrow=TRUE))

@@

```{r,eval=save_figures, fig.height=14, fig.width=9}

@@

plt1 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 7) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  # geom_point(aes(y=state_name,x=exp_cases_median/positive),
  #            color = "darkred", size=.8, alpha=.5) +
  theme_c() + 
  theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Alpha Wave",
       subtitle = "March 26, 2021 through April 8, 2021") +
  xlim(0,65)

@@

plt2 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 13) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  # geom_point(aes(y=state_name,x=exp_cases_median/positive),
  #            color = "darkred", size=.8, alpha=.5) +
  theme_c() + 
 theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Delta Wave",
       subtitle = "June 18, 2021 through July 1, 2021") +
  xlim(0,65)

@@

plt3 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 27) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  theme_c() + 
  theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Omicron Wave",
       subtitle = "December 31, 2021 through January 14, 2022") +
  xlim(0,65)

@@

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning=FALSE,cache=TRUE)

@@

```{r, fig.height=14, fig.width=12}

comp_state_pal <- c("#247C90", "red")

names(comp_state_pal) <- c('Probabilistic Bias Analysis', "Covidestim")

subset %>%
   # mutate(vlabel = gsub("$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$",
   #                     "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", as.character(vlabel))) %>% 
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill = 'Probabilistic Bias Analysis'),
             alpha = .8,
             show.legend=FALSE) +
  geom_ribbon(aes(x = date,
                  fill = 'Covidestim',
                  ymin = infections.lo,
                  ymax = infections.hi),
              alpha = .6) +
  facet_wrap(~name, ncol=4, scales = "free",
              labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_y_continuous(labels = comma) +
  scale_x_date(date_breaks = "3.5 months", 
               date_labels = "%b %Y") +
  theme_c(axis.text.x=element_text(size=7),
          axis.text.y = element_text(size=4.5),
          legend.position = "top",
          legend.text=element_text(size=12),
          strip.text.x=element_text(size=11,
                                    face='plain',
                                    color='white')) +
  scale_fill_manual(values =comp_state_pal, name='')  +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by State")) +
  guides(color = guide_legend(override.aes = list(linewidth =2),
                              nrow=2,
                              byrow=TRUE))

@@

```{r,eval=save_figures, fig.height=14, fig.width=12}

@@

max_val <- subset %>% 
  # left_join(codes) %>%
  filter(biweek %in% c(7, 13,27)) %>%
  mutate(ratio=exp_cases_ub/positive) %>%
  pull(ratio) %>%
  max()

plt1 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 7) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  # geom_point(aes(y=state_name,x=exp_cases_median/positive),
  #            color = "darkred", size=.8, alpha=.5) +
  theme_c() + 
  theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Alpha Wave",
       subtitle = "March 26, 2021 through April 8, 2021") +
  xlim(0,max_val+2)

@@

plt2 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 13) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  # geom_point(aes(y=state_name,x=exp_cases_median/positive),
  #            color = "darkred", size=.8, alpha=.5) +
  theme_c() + 
 theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Delta Wave",
       subtitle = "June 18, 2021 through July 1, 2021") +
  xlim(0,max_val+2)

@@

plt3 <- subset %>% 
  # left_join(codes) %>%
  filter(biweek == 27) %>%
  ggplot(aes(y =fct_reorder(name,exp_cases_median/positive),
             xmin = exp_cases_lb/positive,
             xmax = exp_cases_ub/positive)) +
  geom_errorbar() +
  theme_c() + 
  theme(axis.text.y=element_text(size=10),
        axis.text.x = element_text(size=11),
        axis.title = element_text(size = 17),
        plot.subtitle = element_text(size=14),
        plot.title = element_text(size=17, face="plain")) +
  labs(y="", x="Ratio of Estimated Infections\nto Observed",
       title ="During Two-week Period\nin the Omicron Wave",
       subtitle = "December 31, 2021 through January 14, 2022") +
  xlim(0,max_val+2)

@@

cat("Time interval with the highest ratio of estimated cases to observed: ")

subset %>%
  group_by(biweek) %>%
  mutate(ratio=exp_cases_median/positive) %>%
  summarize(mean_ratio=mean(ratio),
         date = paste(range(date),collapse=" to ")) %>%
  slice_max(n=1, order_by=mean_ratio)

@@

# Summer Testing Rate

subset %>% 
  mutate(testrate = total/population) %>%
  group_by(biweek) %>% 
  mutate(m = median(testrate),
            date=min(date)) %>%
  ggplot(aes(x=date,y=testrate, group=state)) +
  geom_line(alpha=.2) +
  geom_line(aes(y=m, color='Median'), size=2) +
  labs(y = "Total Number of Tests\nOver Population Size",
       title ="Testing Rate Over Time",
       x="") +
  theme_c() +
  theme(axis.title.x = element_text(size=16),
          axis.title.y  = element_text(size=16),
        legend.position='top') +
  geom_vline(xintercept = ymd("2021-07-16"), linetype = 2, linewidth=.5) +
  geom_vline(xintercept = ymd("2021-06-18"), linetype = 2, linewidth=.5) +
  scale_x_date(date_breaks="2 months",
               date_labels = "%b %Y") +
  scale_color_manual(values=c(Median="darkred"),name='')

ggsave(here('figures/testrate-low-summer.pdf'), height=6,width=12, dpi=400)

@@

# Variant Data

```{r, fig.heihgt=7}

m <- state_res %>%
  filter(state == "MI" & version=="v7") %>%
  pull(exp_cases_ub) %>%
  max()

variant <- tar_read(variant, store =targets_dir)

varpal <- c("#7BD8DA","#709f0f", "#e71761", "#9245c8", 
            "#97481c", "#5054b1", "#DA7BA8", "#26B392")

state_res %>%
  filter(state == "MI" & version %in% c("v7")) %>%
 # filter(state %in% sample(corrected$state,5)) %>%
  filter(biweek >=6) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub),
             fill = "#3E3D3D",
             alpha = .5,
             show.legend=FALSE) +
  # geom_ribbon(aes(x = date,
  #                 fill = 'Covidestim',
  #                 ymin = infections.lo,
  #                 ymax = infections.hi),
  #             alpha = .5) +
  # facet_grid(~vlabel, scales = "free_y",
  #             labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(legend.position="top") +
  # theme_c(axis.text.x = element_text(size = 16),
  #         axis.title.y = element_text(size=13),
  #         plot.title=element_text(face = "bold",
  #                                 hjust = .5, 
  #                                 size = 24,
  #                                 margin=margin(5,5,15,5,'pt')),
  #         strip.background = element_rect(fill = "#393939"),
  #         strip.text = element_text(color =  "white", size = 16),
  #         strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
  #                                     size = 22,
  #                                     face="bold"),
  #         strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
  #                                      face = "bold",
  #                                      size = 22),
  #         plot.subtitle = ggtext::element_markdown(size = 25,margin = margin(3,5,10,5,'pt'),
  #                                      face = "italic"),
  #         legend.position = "top",
  #         legend.text =element_text(size = 17),
  #         legend.title = element_text(size=18, face="bold")) +
  geom_line(aes(x=week, y=share*m,
                color =variant_category,
                group=variant_category),
            data=variant,
            linewidth=1.3) +
  # scale_fill_manual(values =pal,
  #                   labels = TeX(names(pal)),
  #                    breaks='Covidestim',
  #                   name='')  +
  scale_y_continuous(sec.axis = sec_axis( trans=~./m, name="Variant Proportion"),
                     labels = comma) +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by Version in Michigan"),
       color = "SARS-CoV-2 Variant",
       x="Date") +
  guides(color = guide_legend(override.aes = list(linewidth =3),
                              ncol=2,title.position="top")) +
 # scale_color_brewer(palette="Accent") 
  scale_color_manual(values=varpal)

ggsave(here('figures/michigan_variant.pdf'), dpi=400)
